Graph Neural Networks For Multi-Image Matching

### 2019-11-13 latex/iclr2020/main.tex
Updated tex file for rebuttal

\usepackage{subcaption}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}

@@

\subsection{Multi-image Matching}
Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section \ref{sec:cycconsist}).
\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
However, the assumption of low Gaussian noise is not realistic.
\cite{zhou2015multi} and \cite{wang2017multi} use more sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
Moving away from feature matching, \cite{zach2010disambiguating} uses cycle-consistency-like constraints on pose graphs quite effectively.
To the best of our knowledge, we are the first to use graph neural networks for multi-image matching.

\subsection{Deep Learning for Matching}
Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets such as \cite{zagoruyko2015learning}; \cite{yi2016lift}; and \cite{brachmann2017dsac}.
This approach is limited if one does not have the ability to get the ground truth correspondences.
There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
Like us \cite{zhu2017unpaired} use cycle consistency in their loss; however their method is for image generation and is restricted to pairwise cycle consistency.
Our method can be applied to 3 or more images. 
\cite{hartmann2017learned} learns multi-image matching but requires heavy supervision from 3D object reconstructions, which can be difficult or expensive to obtain.

@@

This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
\begin{equation}
\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
\end{equation}
Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
Note that because of this formulation, we can determine our embeddings only up to a rotation, as
$ \mF_V R(\mF_V R)^\top
= \mF_V RR^\top \mF_V^\top
= \mF_V\mF_V^\top
\label{eq:rotinvar} $
Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).

@@

\begin{table*}[t]
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Method & Same Point Similarities & Different Point Similarities  \\
\hline\hline\hline
Ideal                              & 1.00e+0 $\pm$ 0.00e+0 & 0.00e+0 $\pm$ 0.00e+0 \\ \hline
Initialization Baseline            & 5.11e-1 $\pm$ 1.68e-2 & 2.56e-1 $\pm$ 2.06e-1 \\ \hline
5 Views, Noiseless                 & 1.00e+0 $\pm$ 4.15e-4 & 1.22e-1 $\pm$ 1.67e-1 \\ \hline
6 Views, Added Noise               & 9.84e-1 $\pm$ 3.16e-2 & 7.46e-2 $\pm$ 1.57e-1 \\ \hline
3 Views, 5\% Outliers              & 9.29e-1 $\pm$ 1.79e-1 & 1.41e-1 $\pm$ 1.48e-1 \\ 
3 Views, 10\% Outliers             & 9.27e-1 $\pm$ 1.79e-1 & 1.40e-1 $\pm$ 1.51e-1 \\ \hline

>>>>

\usepackage{subcaption}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor}

@@

\subsection{Multi-image Matching}
Multi-image matching has traditionally been done using optimization based methods minimizing a cycle consistency based loss (see Section \ref{sec:cycconsist}).
\cite{pachauri2013solving} and \cite{arrigoni2017synchronization} use the eigenvectors of the matching matrix to obtain a low dimensional embedding. 
However, the assumption of low Gaussian noise is not realistic.
\cite{zhou2015multi} and \cite{wang2017multi} use more sophisticated optimization techniques on the matching matrix and thus produce more robust solutions.
\cite{leonardos2016distributed} implement a distributed optimization scheme to solve for cycle consistency.
\textcolor{red}{\cite{swoboda2019convex} implement a convex relaxation of the low dimensional embedding problem.}
\textcolor{red}{\cite{shi2016tensor} use tensor power iterations to solve the matching problem, also taking into account the intra-image matching graph.}
As an alternative to optimization based techniques, \cite{tron2017fast} used density based clustering techniques to compute multi-image correspondence.
Moving away from feature matching, \cite{zach2010disambiguating} uses cycle-consistency-like constraints on pose graphs quite effectively.
To the best of our knowledge, we are the first to use graph neural networks for multi-image matching.

\subsection{Deep Learning for Matching}
Previous attempts to improve image matching techniques using machine learning have focused on learning the descriptors given ground truth correspondence from curated datasets such as \cite{zagoruyko2015learning}; \cite{yi2016lift}; and \cite{brachmann2017dsac}.
This approach is limited if one does not have the ability to get the ground truth correspondences.
There are other methods to build correspondences such as \cite{choy2016universal}, but they only handle two-view constraints and require dense correspondences.
Most similar to our work, \cite{yi2018learning} attempts to improve correspondences by learning match probabilities for two-view RANSAC for greater robustness and speed.
Like us \cite{zhu2017unpaired} use cycle consistency in their loss; however their method is for image generation and is restricted to pairwise cycle consistency.
Our method can be applied to 3 or more images. 
\cite{hartmann2017learned} learns multi-image matching but requires heavy supervision from 3D object reconstructions, which can be difficult or expensive to obtain.
\textcolor{red}{\cite{zhou2015flowweb}, unlike our method, uses dense correspondence, but uses cycle consistency to find semantic matches accross multiple views.}
\textcolor{red}{\cite{suwajanakorn2018discovery} find 3 dimensional latent keypoints, trained using ground truth rotation and translation. However, their method is restricted to a limited number of object categories, which is different from the SfM setting we are considering here.}

@@

This reduces the number of our constraints from $O(n^3)$ to $O(n^2)$.
\textcolor{red}{This was shown to be equivalent to the original definition of cycle consistency (equation \ref{eq:cycconsist1}) in \cite{huang2013consistent}.}
We try to learn vertex embeddings $\mF_V$ to approximate $\mX$ - in other words the final embedding should be an encoding of the universe of features.
As we do not have the ground truth matches $\mM$, we approximate it using the noisy adjacency matrix $\mA$ of our correspondence graph. Thus our loss would be 
\begin{equation}
\mathcal{L}(\mA, \mF_V) = \mathcal{D}(\mA, \mF_V \mF_V^\top)
\end{equation}
Here $\mathcal{D}$ could be an $L_2$ loss, $L_1$ loss, or many others. In this work, we use the $L_1$ loss. 
Note that because of this formulation, we can determine our embeddings only up to a rotation, as
$ \mF_V R(\mF_V R)^\top
= \mF_V RR^\top \mF_V^\top
= \mF_V\mF_V^\top
\label{eq:rotinvar} $
Thus when visualizing embeddings, we rotate them to make them more interpretable (see figure \ref{fig:embeddingsviz}).

@@

\begin{table*}[t]
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
Method & Same Point Similarities & Different Point Similarities  \\
\hline\hline\hline
Ideal                              & \textcolor{red}{1.000} $\pm$ \textcolor{red}{0.0000} & \textcolor{red}{0.0000} $\pm$ \textcolor{red}{0.0000} \\ \hline
Initialization Baseline            & \textcolor{red}{0.511} $\pm$ \textcolor{red}{0.0168} & \textcolor{red}{0.2560} $\pm$ \textcolor{red}{0.2060} \\ \hline
5 Views, Noiseless                 & \textcolor{red}{1.000} $\pm$ \textcolor{red}{0.0004} & \textcolor{red}{0.1220} $\pm$ \textcolor{red}{0.1670} \\ \hline
6 Views, Added Noise               & \textcolor{red}{0.984} $\pm$ \textcolor{red}{0.0031} & \textcolor{red}{0.0746} $\pm$ \textcolor{red}{0.1570} \\ \hline
3 Views, 5\% Outliers              & \textcolor{red}{0.929} $\pm$ \textcolor{red}{0.1790} & \textcolor{red}{0.1410} $\pm$ \textcolor{red}{0.1480} \\ 
3 Views, 10\% Outliers             & \textcolor{red}{0.927} $\pm$ \textcolor{red}{0.1790} & \textcolor{red}{0.1400} $\pm$ \textcolor{red}{0.1510} \\ \hline
